%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer - MSAI (Search, Assistant \& Intelligence)} % Job title
    {Microsoft} % Organization
    {Santiago, Chile} % Location
    {Jan. 2024 - Sep. 2025} % Date(s)
    {
        \begin{cvitems}
            % --- CDAC ---
            \item {
                Architected CDAC (Certification Detection and Control), a distributed early warning system designed to modernize the quality assurance pipeline for M365 Search products (Word, PowerPoint, Outlook, SharePoint, etc).
                  \begin{itemize}
                    \item {Revolutionized the regression testing process by replacing weeks-long A/B testing telemetry collection cycles with advanced statistical analysis techniques.}
                    \item {Reduced metric regression detection time to just 6 hours, preventing code rewrites and safeguarding search quality while meeting the aggressive deployment demands of the Copilot era.}
                  \end{itemize}
            }
            % --- LSS ---
            \item {
              Engineered core features for LSS (Local Shard Search), a high-concurrency microservice serving as the critical bridge between Search APIs and global storage shards, handling over 200M daily requests.
              \begin{itemize}
                \item {Led the development of exclusive search capabilities for Microsoft Copilot, enabling access to new data indices and advanced query patterns that significantly enriched AI-generated responses for complex document analysis.}
                \item {Developed internal LLM-based autonomous agents to analyze telemetry and diagnose incidents, reducing manual on-call operational load by approx. 50\% and streamlining system maintenance.}
                \item {Optimized critical low-latency components by migrating legacy code from C\# to Rust, significantly improving throughput and resource efficiency.}
                \item {Maintained high availability for mission-critical search infrastructure, performing on-call rotations for a large-scale production environment.}
              \end{itemize}
            }
            % --- STACK ---
            \item {Technologies used: C\#, .NET, Rust, Python, KQL, Azure, Internal LLM Tools.}
        \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Director of Engineering LATAM} % Job title
    {Nezasa} % Organization
    {Santiago, Chile} % Location
    {Sep. 2022 - Sep. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the technology areas merger between TripYeah and Nezasa, ensuring efficient integration.}
        \item {Coordinated and planned activities for teams across LATAM, optimizing resources and timelines.}
        \item {Directed the integration of TripYeah (now TripOptimizer) into Nezasa's product suite, significantly enhancing the itinerary creation process.}
        \item {Implemented an innovative chatbot using OpenAI's API, improving the travel itinerary creation interface.}
        \item {Handled incident resolution and development of advanced functionalities.}
        \item {Technologies used: TypeScript, ReactJS, NextJS, Golang, Python, Kubernetes, Skaffold, Kafka, gRPC, Protobuf, AWS, OpenAI APIs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder \& CTO} % Job title
    {TripYeah [Acquired by Nezasa]} % Organization
    {Santiago, Chile} % Location
    {Apr. 2021 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coordinated developments among distributed teams in Latin America.}
        \item {Designed event-driven microservices architecture to solve complex multi-destination itinerary problems, integrating real-time flight prices from providers like Amadeus or Sabre.}
        \item {Significantly improved the efficiency of recommendations (multi-destination itinerary with real-time prices), reducing times from 90 to 10 seconds using patterns like CQRS and event-driven architecture.}
        \item {Developed Full Stack solutions and led the resolution of incidents and complex developments.}
        \item {Mentored trainee engineers and contributed to raising capital (+2m USD) and the company's sale.}
        \item {Technologies used: TypeScript, ReactJS, NextJS, Golang, Python, Kubernetes, Skaffold, Kafka, gRPC, Protobuf, Redis, AWS.}
      \end{cvitems}
    }
\end{cventries} 
\newpage 
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist and Tech Leader} % Job title
    {Globant} % Organization
    {Santiago, Chile} % Location
    {Nov. 2019 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the Augmented Design team in the Augmented Globant initiative (now Globant X), focusing on the development of an innovative UX usability testing platform. This platform was distinguished by its ability to capture facial data, voice tone, and eye tracking, enabling advanced user interaction statistics.}
        \item {Responsible for planning, creating, and implementing advanced machine learning and deep learning models, specialized in recognizing facial expressions and emotions in voice tones, as well as generating heatmaps through eye tracking.}
        \item {Closely collaborated with the Product Manager in the software development planning, ensuring project objectives alignment.}
        \item {Played a key role as a Full Stack Developer, contributing to the platform's comprehensive development.}
        \item {Participated in presentations and pre-sales in Brazil and Chile, representing Globant's data science studio.}
        \item {Awarded a direct categorization from Semi-Senior to Senior (skipping Semi-Senior Advance) during the first year, due to good evaluations and project management.}
        \item {Technologies used: TypeScript, ReactJS, Golang, Python, TensorFlow, TF.JS, Docker, Docker-compose, AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Full Stack Developer} % Job title
    {Ticketplus.cl} % Organization
    {Santiago, Chile} % Location
    {Mar. 2015 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and operated an innovative event ticketing platform, optimizing user experience and sales process efficiency.}
        \item {Direct interaction with clients for product improvement and customization.}
        \item {Led the planning and execution of new features and functionalities, significantly enhancing the platform's service offerings.}
        \item {Implemented an efficient event door validation system, ensuring agile and secure access management.}
        \item {Designed and introduced an online queuing system for mass purchase attention, improving high-volume traffic and sales handling capacity.}
        \item {Technologies used: JavaScript, AngularJS, Ruby on Rails, Redis, AWS.}
      \end{cvitems}
    }

\end{cventries}
